%%% Seznam použité literatury je zpracován podle platných standardů. Povinnou citační
%%% normou pro bakalářskou práci je ISO 690. Jména časopisů lze uvádět zkráceně, ale jen
%%% v kodifikované podobě. Všechny použité zdroje a prameny musí být řádně citovány.

\def\bibname{Bibliography}
\begin{thebibliography}{99}
\addcontentsline{toc}{chapter}{\bibname}

\bibitem{szeliski2010} 
  {\sc R. Szeliski.}
  \emph{Computer Vision: Algorithms and Applications.}
  Springer, 2010. 

\bibitem{snavely2008}
  {\sc Noah Snavely and Rahul Garg and Steven M. Seitz and Richard Szeliski.} 
  \emph{Finding Paths through the World's Photos.}
  % number  = {3},
  % pages   = {11-21}

\bibitem{cnnsynth}
  \emph{The 44\textsuperscript{th} President Inauguration.}
  CNN, Inc., 2013. Accessible from \url{http://www.cnn.com/themoment}, retrieved on 2013-07-01.

\bibitem{surf2006}
  {\sc  H. Bay, A. Ess, T. Tuytelaars, and L. Van Gool.}
  \emph{Speeded–Up Robust Features (SURF).}
  In ECCV, 2006.

\bibitem{ransac}
  {\sc M. A. Fischler, and R. C. Bolles.} 
  \emph{Random sample consensus: A paradigm for model fitting with applications to image analysis and automated cartography.} 
  In Communications of the ACM, 24(6): 381-395, 1981.

\bibitem{harris1988}
  {\sc C. Harris and M. Stephens.} 
  \emph{A combined corner and edge detector.}
  In Proceedings of the Alvey Vision Conference, pages 147 – 151, 1988.

\bibitem{multipleview}
  {\sc  R. Hartley, A. Zisserman.}
  \emph{Multiple View Geometry in Computer Vision.}
  Cambridge University Press, 2003.

\bibitem{hirschmuller2008}
  {\sc  H. Hirschmüller}
  \emph{Stereo Processing by Semiglobal Matching and Mutual Information}
  Pattern Analysis and Machine Intelligence, 2008. IEEE Transactions on.

\bibitem{marketshare}
  IDC Worldwide Mobile Phone Tracker, 2013. IDC, 2013.

\bibitem{siftsurf2009}
  {\sc L. Juan and O. Gwun.} 
  \emph{A Comparison of SIFT, PCA-SIFT and SURF.}
  In International Journal of Image Processing (IJIP), 2009.

\bibitem{jurie2004}
  {\sc F. Jurie and C. Schmid.} 
  \emph{Scale–invariant shape features for recognition of object categories.}
  In CVPR, volume II, pages 90 – 96, 2004.

\bibitem{kadir2001}
  {\sc T. Kadir and M. Brady.} 
  \emph{Scale, saliency and image description.}
  IJCV, 45(2):83 – 105, 2001.

\bibitem{siftsurf2001}
  {\sc N. Y. Khan, B. McCane, and G. Wyvill.} 
  \emph{SIFT and SURF Performance Evaluation Against Various Image Deformations on Benchmark Dataset.}
  On International Conference on Digital Image Computing: Techniques and Applications, 2001.

  
\bibitem{lindeberg1998}
  {\sc T. Lindeberg.} 
  \emph{Feature detection with automatic scale selection.}
  In International Journal of Computer Vision, 30(2):79 – 116, 1998.

\bibitem{lowe1999}
  {\sc D. Lowe.} 
  \emph{Object recognition from scale–invariant features.}
  In CCV, 1999.

%\bibitem{roy1998}
%  {\sc S. Roy.} 
%  \emph{A Maximum-Flow Formulation of the N-camera Stereo Correspondence Problem.}
%  Computer Vision, 1998. Sixth International Conference on.

\bibitem{lucas}
  {\sc B. D. Lucas and T. Kanade. } 
  \emph{An iterative image registration technique with an application to stereo vision.}
  In Proceedings of Imaging Understanding Workshop, 121--130, 1981.

\bibitem{roy1999}
  {\sc S. Roy.} 
  \emph{Stereo Without Epipolar Lines: A Maximum-Flow Formulation.}
  In International Journal of Computer Vision, 1999.

\bibitem{snavely2007}
  {\sc N. Snavely; S. M. Seitz; R. Szeliski.} 
  \emph{Modeling the world from Internet photo collections.}
  In International Journal of Computer Vision, 2007.

\bibitem{snavely2006}
  {\sc N. Snavely; S. M. Seitz; R. Szeliski.} 
  \emph{Photo tourism: Exploring photo collections in 3D.}
  ACM Transactions on Graphics (SIGGRAPH Proceedings), 25(3), 2006, 835-846.

\bibitem{snavely2008}
  {\sc N. Snavely; S. M. Seitz; R. Szeliski.} 
  \emph{Skeletal graphs for efficient structure from motion.}
  Computer Vision and Pattern Recognition, 2008. CVPR 2008. IEEE Conference on.


%\bibitem{lamport94}
%  {\sc Lamport,} Leslie.
%  \emph{\LaTeX: A Document Preparation System}.
%  2. vydání.
%  Massachusetts: Addison Wesley, 1994.
%  ISBN 0-201-52983-1.

\end{thebibliography}
